Tables

### 2019-04-25 code/tables.rmd
Cleaned up helper function R-file and tables.rmd a little

#Transform effect sizes to raw correlations
#'transform_MA' is a sourced function
dat2 <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe

#estimate tau2 for tranformed biserial and pearson's correlations
#'summarizer' is a sourced function
res2 <- dat2 %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect")

>>>>

#Transform effect sizes to biserial correlations (pearson's correlations left as is)
#estimate tau2 for correlations
#'transform_MA' and 'summarizer' are sourced functions
res2 <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA) %>% #
  map_dfr(summarizer, .id = "effect")
